---
title: "Introduction to DBmaps"
author: "DIVENDRA SINGH YADAV"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to DBmaps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction

The `DBmaps` package provides tools for exploring, mapping, and merging tables in a relational database. This vignette demonstrates how to use the key functions in the package: `create.DB.map`, `multi.merge`, and `visualize.DB.map`.

## Example: Creating a Database Map

The `create.DB.map` function constructs a map of relationships between tables in a database. It specifies which tables can be joined, the linking variables, the type of join, and optional aggregations.

```{r setup, include=FALSE}
library(DBmaps)
library(data.table)
library(ggplot2)
```

## Creating a Database Map (`create.DB.map`)

The `create.DB.map()` function helps visualize relationships between tables in a database.

```{r}
# Define example tables
table1 <- data.table(id = c(1, 2), value1 = c("A", "B"))
table2 <- data.table(id = c(2, 3), value2 = c("C", "D"))
table3 <- data.table(id = c(3, 4), value3 = c("E", "F"))

# Define relationships between tables
relationships <- list(
  list(table1 = "table1", table2 = "table2", key = "id", type = "inner"),
  list(table1 = "table2", table2 = "table3", key = "id", type = "left")
)

# ✅ Use a named list for tables
db_map <- create.DB.map(tables = list(
  table1 = table1,
  table2 = table2,
  table3 = table3
),
by = list(
    list(table1 = "table1", table2 = "table2", by.x = "id", by.y = "id"),
    list(table1 = "table2", table2 = "table3", by.x = "id", by.y = "id")
  )
)

# Print map summary
print(db_map)
```

## Merging Tables (`multi.merge`)

The `multi.merge()` function merges multiple tables based on specified keys and join types.

```{r}
# Merge tables using inner and left joins
merged_result <- multi.merge(
  tables = list(
    table1 = table1,
    table2 = table2,
    table3 = table3
  ),
  by = "id",
  types = c("inner", "left")
)

# View the merged result
print(merged_result)

```

## Visualizing Database Relationships (`visualize.DB.map`)

The `visualize.DB.map()` function creates a graphical representation of the database schema.

```{r}
# Visualize database map
visualize.DB.map(db_map)
```
